Death By Dropdown?

### 2025-04-08 conference-materials/2025_shiny-conf/slides.qmd
Refactors reactable example for consistency
- Aligns {reactable} implementation with screenshot example.
- Updates dynamic legend to example.
- Updates dependencies in example.

@@

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "4-14|15-50"

# Packages: reactable, dplyr, bslib
reactable(
  soundpulse_data,
  # Stage 3: Group related elements (Principle of Proximity)
  columnGroups = list(
    colGroup(
      name = "Core Metrics",
      columns = c("Metric 1", "Metric 2", "Metric 3", "Metric 4")
    ),
    colGroup(
      name = "Key Performance",
      columns = c("KPI 1", "KPI 2", "KPI 3")
    )
  ),
  # Stage 1: Visual indicators for headers 
  # (simplification of Hick's Law dynamic legend)
  defaultColDef = colDef(
    header = function(value) {
      layout_inline(
        value,
        span(
          style = css(
            display = "inline-block",
            margin_left = "5px",
            height = "10px", 
            width = "10px",
            border_radius = "50%",
            background_color = "#1c6d7d"
          )
        )
      )
    }
  ),
  # Combine multiple visual elements for age groups
  columns = list(
    Age = colDef(
      cell = function(value) {
        colors <- c(
          "18-24" = "#1c6d7d",
          "25-34" = "#35a4ae", 
          "35-44" = "#98d3ca",
          "45-54" = "#ffca90",
          "55-64" = "#1c6d7d",
          "65-74" = "#dd8500"
          )

        span(value, style = css(color = colors[value], font_weight = "bold"))
      }
    )
  )
)
```

>>>>

<!-- TODO: replace title background image with css and brand elements -->

@@

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "2-10|12-16|17-27|29-38|39|40-56"

# Packages: reactable, purrr
# Define age group colors for consistency
age_colors <- c(
  "18-24" = "#1c6d7d",
  "25-34" = "#35a4ae", 
  "35-44" = "#98d3ca",
  "45-54" = "#ffca90",
  "55-64" = "#1c6d7d",
  "65-74" = "#dd8500"
)

# Create the table with dynamic legend component
div(
  # Main table component
  reactable(
    soundpulse_data,
    # Stage 3: Group related elements (Principle of Proximity)
    columnGroups = list(
      colGroup(
        name = "Core Metrics",
        columns = c("Metric 1", "Metric 2", "Metric 3", "Metric 4")
      ),
      colGroup(
        name = "Key Performance",
        columns = c("KPI 1", "KPI 2", "KPI 3")
      )
    )
  ),
  # Stage 1: Dynamic legend (Hick's Law - reduces choice complexity)
  div(
    style = css(
      display = "flex",
      align_items = "center",
      margin_top = "10px",
      padding = "8px",
      border_radius = "4px",
      background_color = "#f9f9f9"
    ),
    map(names(age_colors), function(age_group) {
      div(
        style = css(
          display = "flex", 
          align_items = "center", 
          margin_right = "15px"
        ),
        div(
          style = css(
            width = "10px", 
            height = "10px", 
            border_radius = "50%", 
            background_color = age_colors[age_group],
            margin_right = "5px"
          )
        ),
        span(age_group)
      )
    })
  )
)
```
